
\clearpage
# MODÈLE BAYÉSIEN HIÉRARCHIQUE AVEC LES DONNÉES SUR LE STOCK-RECRUTEMENT DU SAUMON ROUGE DANS LES RÉSEAUX DE LA RIVIÈRE SKEENA {#app:HBMFits}



```{r,echo=FALSE, message=FALSE}
library(tidyverse)
library(csasdown)

HBM.results <- readRDS("data/HBM/HBM_appendix_tables.rds")

pasteList <- function(x, suffix=NULL) {
  n <- length(x)
  if (!is.null(suffix)) x <- paste0(x, suffix)
  if(n == 1) return(x)
  a <- paste(head(x, n=(n-1)), collapse = ", ")
  paste(c(a, tail(x, 1)), collapse = ", and ")
}
# str(HBM.results)

# TASKS
# - Standardize terms: lognormal or log-normal,  capitalize Normal?
# - methods - include JAGS
# - [ ] prettyNum
# -[ ] intro to sensitivity
# - [ ] Citations
# - [ ] shrinkage 
# - [ ] Umsy definition
```

<!-- 
Questions

Normal draws were defined in terms of precision, does the remainder of the document

See equation \@ref(eq:HBMLinRick)
-->

**Annexe fournie par Murdoch McAllister et Wendell Challenger**

*Remarque : Cette annexe est une contribution autonome au document de recherche. Elle a été incluse comme contre-vérification des résultats clés (p. ex. scénarios de productivité) et pour établir un lien entre les analyses des géniteurs-recrues d’un seul stock présentées dans le corps du rapport et les travaux antérieurs de @KormanEnglish2013, qui ont utilisé une approche bayésienne hiérarchique. Cette annexe applique l’approche de @KormanEnglish2013 aux données sur les géniteurs-recrues mises à jour et comprend des tests de sensibilité approfondis pour permettre des comparaisons plus directes avec les ajustements du modèle à un seul stock.*

Un MBH a été élaboré pour l’estimation des paramètres du modèle stock-recrutement de Ricker pour les stocks de saumon rouge du bassin versant de la rivière Skeena. Le temps a manqué pour préparer un MBH pour les stocks du bassin versant de la rivière Nass. Cette structure a été utilisée parce qu’on a supposé que l’échangeabilité du paramètre de la productivité des stocks était limitée aux stocks dans chaque bassin versant. La distribution de la fréquence des caractéristiques du cycle biologique des stocks, comme la composition selon l’âge des géniteurs, la fréquence relative des types de cycle biologique à croissance dans les lacs et autres, les périodes de montaison et les voies de migration en milieu marin sont différentes entre les stocks de saumon rouge dans ces deux bassins versants.  



## FORMULES MATHÉMATIQUES ET STATISTIQUES DU MBH {#app:HBMFits-1}

Les MBH de la rivière Skeena utilisent une forme linéarisée du modèle stock-recrutement de Ricker :


\begin{equation}
\log{\left(\frac{R_{s,y}}{S_{s,y}}\right)=a_s-}\beta_s\cdot\ S_{s,y}+\epsilon_{s,y}
(\#eq:HBMLinRick)
\end{equation}

où $R_{s,y}$ est l’abondance observée des recrues produites dans le stock $s$ l’année d’éclosion $y$ par l’abondance correspondante des géniteurs l’année d’éclosion $S_{s,y}$. Le paramètre $a_s$ est le logarithme naturel du taux maximal d’augmentation de la population, $\beta_s$ est le coefficient propre au stock pour l’effet dépendant de la densité de l’abondance des géniteurs sur la productivité du stock et $\epsilon_{s,y}$ représente le terme d’erreur du stock par année qui est censé avoir une distribution normale.

Le cadre du MBH présenté repose sur celui formulé par @KormanEnglish2013, qui ont estimé les paramètres de stock-recrutement pour de nombreux stocks de saumon dans le réseau de la rivière Skeena. Le MBH suppose, comme @KormanEnglish2013, que le paramètre $a$ de Ricker est échangeable entre les stocks d’un réseau fluvial avec une moyenne hyper a priori et un écart-type hyper a priori :


\begin{equation}
  a_s \sim  \ln \textrm{Normal}\left(\mu_a,\ \tau_a\right) 
\end{equation}

où $\mu_a$ est le logarithme naturel de la médiane hyper a priori du paramètre $a$ de Ricker, et $\tau_a$ est la précision hyper a priori du paramètre $a$ de Ricker. Les valeurs hyper a priori suivantes ont été attribuées à $\mu_a$ et à $\tau_a$ :
  
\begin{equation}
  \mu_a \sim \textrm{Normal}\left({0.5,\ 10^{-6}}\right)
  \textrm{, and }
  \tau_a \sim  \textrm{Gamma} \left(0.5,\ 0.5 \right).
\end{equation}


@KormanEnglish2013 ont choisi ces a priori comme des a priori vagues et nous avons repris les mêmes hyper a priori dans les formules actuelles.

Une valeur a priori log-normale informative a également été supposée pour le paramètre $\beta_s$ de densité-dépendance qui suit la formulation utilisée dans @KormanEnglish2013 :

\begin{equation}
  \beta_s \sim \ln \textrm{Normal}\left(\mu_{\beta,s},\ \tau_{\beta,s}\right)
\end{equation}

où $\mu_{\beta,s}$  a été tiré des résultats d’analyses limnologiques antérieures de la productivité des lacs qui ont évalué l’abondance des géniteurs (c.-à-d. $S_{\textrm{max},s})$ qui pourrait produire en moyenne le nombre maximal de recrues pour chaque stock. Les valeurs $\mu_{\beta,s}$  et $\tau_{\beta,s}$ ont été déterminées comme suit :

  
\begin{equation}
  \mu_{\beta,s}= \log \left(  \frac{1}{S_{\textrm{max},s}} \right)
  \textrm{,  and  } 
  \tau_{\beta,s}=\left(\frac{1}{\sigma_{\textrm{max},s}}\right)^2.
\end{equation}
  
  
 où $\sigma_{\textrm{max},s}$ est l’écart type a priori dans le logarithme naturel de $S_{\textrm{max},s}$. Il faut noter que les valeurs de $\sigma_{\textrm{max},s}$ sont presque identiques au coefficient de variation pour les valeurs plus petites de $\sigma_{\textrm{max},s}$(environ 0,5 et moins) et que, par conséquent, nous utilisons le coefficient de variation et $\sigma_{\textrm{max},s}$ de façon interchangeable pour décrire la précision de la valeur a priori. Cela dit, le rapport entre le coefficient de variation et $\sigma_{\textrm{max},s}$) augmente nettement au-dessus de 1 (c.-à-d. que le coefficient de variation est plus grand que $\sigma_{\textrm{max},s}$) à des valeurs plus grandes de $\sigma_{\textrm{max},s}$, ce qui signifie que le coefficient de variation réel est plus grand que celui indiqué et que la valeur a priori sera plus diffuse. Les valeurs de $S_{\textrm{max},s}$ et de $\sigma_{\textrm{max},s}$ pour chaque stock dans le bassin versant de la rivière Skeena sont indiquées dans le tableau \@ref(tab:PrSmax). 
  
  
<!-- TABLE C.1. Smax Priors -->
```{r PrSmax, echo=FALSE, results='asis'}
cap <- "Médiane des valeurs a priori de $S_\\textrm{max}$  propre au stock et écart type a priori dans le logarithme naturel de $S_\\textrm{max}$ (c.-à-d. $\\sigma_{\\textrm{max},s}$) d’après les résultats d’analyses précédentes de la productivité des lacs. Dans les deux cas où trois stocks sont répertoriés sur la même ligne, les valeurs moyennes de $S_\\textrm{max}$ accessibles ont été ajoutées puisque les différents lacs de croissance de ces stocks étaient géographiquement très proches et les données sur le stock-recrutement pour ces stocks ont donc été combinées en une seule série chronologique de données sur le stock-recrutement pour l’estimation des paramètres de stock-recrutement."


# data.frame(Yes = 1:10, No = LETTERS[11:20]) %>%
HBM.results$Smax %>%
  filter(Basin == "Skeena") %>%
  mutate(prSmax = prettyNum(round(prSmax),big.mark=" ")) %>%
  mutate(prCV= prettyNum(prCV,decimal.mark=",")) %>%
  mutate(Stock = gsub( "Babine Early Wild", "Babine sauvage hâtive" ,Stock)) %>%
   mutate(Stock = gsub( "Babine Late Wild", "Babine sauvage tardive" ,Stock)) %>%
    mutate(Stock = gsub( "Babine Mid Wild", "Babine sauvage moyenne" ,Stock)) %>%
  rename(
     Lac = Lake,
	 Bassin = Basin,
    `$S_{\\textrm{max},s}$` = prSmax,
    `CV/$\\sigma_{\\textrm{max},s}$` = prCV
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l","l", "l", "r", "r"),
    caption = cap
  )
```

Les valeurs de $\sigma_{\textrm{max},s}$ ont été tirées, pour la plupart des stocks de saumon rouge de la rivière Skeena, de @KormanEnglish2013). Il convient de noter qu’une valeur de 2,00 pour $\sigma_{\textrm{max},s}$  rend la valeur a priori correspondante de $S_{\textrm{max},s}$ vague et diffuse. Par exemple, par rapport à la médiane, les limites inférieures et supérieures des intervalles de crédibilité à 95 % seraient environ cinquante fois plus basses et cinquante fois plus élevées que la médiane. Dans les cas où la valeur de  $\sigma_{\textrm{max},s}$ a été fixée à 2,00, au moins certains membres du groupe de travail ont soulevé des préoccupations au sujet de la base empirique des valeurs de $S_{\textrm{max},s}$  que l’on pourrait obtenir pour ces stocks. Les stocks du lac Babine représentaient un regroupement de stocks qui a été divisé en cinq, celui de la rivière Asitka reposait sur une approximation et celui de la rivière Morice était un réseau de deux lacs dont seul le plus grand a été mesuré. En raison de ces problèmes, nous avons utilisé des valeurs a priori diffuses pour ces stocks.

Au moment de l’analyse, aucune estimation de la productivité du lac n’était disponible pour la rivière Asitka. De ce fait, une approximation brute de la médiane a priori de $S_{\textrm{max},s}$ pour la rivière Asitka a été tirée du produit de la superficie du lac pour la rivière Asitka et de la moyenne de $S_{\textrm{max},s}$ par unité de superficie du lac pour les lacs du bassin versant de la rivière Skeena pour lesquels des estimations de $S_{\textrm{max},s}$ pour le saumon rouge étaient accessibles. En raison de la grande incertitude entourant $S_{\textrm{max},s}$ pour le stock de la rivière Asitka, nous avons supposé une valeur de 2,00 pour $\sigma_{\textrm{max},s}$  de ce stock, ce qui en fait une valeur a priori vague.

Pour les cinq stocks du lac Babine, une grande incertitude entoure la capacité des lacs pour chaque stock en raison de l’incertitude concernant la façon dont la ressource commune est partagée entre les cinq stocks étant donné que les juvéniles d’au moins cinq des stocks reconnus du lac Babine grandissent dans le lac. La médiane a priori de $S_{\textrm{max},s}$ pour chacun des cinq stocks du lac Babine a été calculée en divisant l’estimation de la productivité totale du lac Babine par cinq, ce qui donne une répartition égale de la ressource partagée pour chaque stock du lac Babine. Étant donné que la proportion réelle de la productivité du lac utilisée par chaque stock demeure inconnue, un niveau élevé d’incertitude (c.-à-d. une valeur de 2,00 de $\sigma_{\textrm{max},s}$) a été attribué à chaque stock du lac Babine.

Comme dans @KormanEnglish2013, nous avons appliqué une fonction de vraisemblance normale dans le MBH et la même valeur a priori à l’écart type des écarts entre la productivité prévue et la productivité observée :


\begin{equation}
  \log{\left(\frac{R_{s,y}}{S_{s,y}}\right) \sim   \textrm{Normal}\left(\mu_{s,y}^{RS},\  \tau_s \right)} 
\end{equation}

où $\log(R_{s,y}/S_{s,y})$ est le logarithme naturel observé du ratio des recrues produites par les géniteurs (c.-à-d. la productivité) l’année d’éclosion $y$ pour le stock $s$, $\mu_{s,y}^{RS}$ est la productivité propre au stock prévue par le modèle stock-recrutement de Ricker (voir l’équation (\@ref(eq:HBMLinRick))), conditionné par les paramètres $a_s$ et $\beta_s$, et $\tau_s$  est la précision propre au stock utilisée dans la fonction de vraisemblance et donnée par la formule 

\begin{equation}
  \tau_s=\frac{1}{\sigma_s^2}
\end{equation}
 
où $\sigma_s$ est l’écart type propre au stock dans les écarts entre la productivité observée et la productivité prévue. La valeur a priori pour $\sigma_s$ est la même que celle appliquée dans @KormanEnglish2013 : 


\begin{equation}
  \sigma_s \sim \textrm{Uniform}(0.05,\ 10).
\end{equation}

Le MBH original de @KormanEnglish2013 ne tenait pas compte des variations temporelles de la productivité; comme ce point présentait un intérêt dans l’étude actuelle, nous avons étendu le MBH de @KormanEnglish2013 pour inclure un effet annuel commun sur la productivité du stock (c.-à-d. $\log(R_{s,y}/S_{s,y})$). On pose l’hypothèse qu’en raison de la proximité spatiale des stocks de saumon rouge dans un bassin versant (celui de la rivière Skeena) et le chevauchement entre les stocks dans les voies de migration en eau douce et en mer, la productivité annuelle de différents stocks s’écartera des prévisions du modèle de Ricker dans le même sens et d’une ampleur semblable chaque année. Ainsi, en plus d’un écart propre au stock entre la prévision de la productivité dans le modèle de Ricker et la productivité observée, un écart ou un effet annuel commun a également été inclus dans le MBH. La forme linéarisée du modèle de Ricker qui comprend l’effet annuel commun $T_y$ l’année $y$ est donc donnée par la formule :

\begin{equation}
  \mu_{s,y}^{RS}=a_s-\beta_s\cdot S_{s,y}+T_y
\end{equation}
  
La valeur a priori de $T_y$ est donnée par la formule :


\begin{equation}
  T_y \sim \textrm{Normal}\left(0,\ \tau_T\right)
\end{equation}
  
 où $\tau_T$ est la précision a priori dans l’effet annuel commun, qui est calculée comme $\tau_T=1/\sigma_T^2$, avec $\sigma_T$  représentant l’écart type dans les effets annuels communs. La valeur hyper a priori pour $\sigma_T$  a été déterminée comme suit : 
  

\begin{equation}
  \sigma_T \sim \ln \textrm{Normal} \left(\log{\left(0.8\right),\ \frac{1}{{0.7}^2}}\right).
\end{equation}


La valeur a priori de  $\sigma_T$ a été choisie de manière à être légèrement informative avec la tendance centrale a priori et la précision a priori établies à des valeurs qui permettent aux données d’informer une vaste fourchette de valeurs et de tenir compte d’une variation interannuelle potentiellement importante des effets annuels communs.

L’estimation des effets annuels communs devrait représenter les écarts moyens par rapport aux prévisions de la productivité du stock par le modèle de Ricker pour l’ensemble des stocks une année donnée. L’effet annuel commun pourrait résulter de taux de survie supérieurs ou inférieurs à la moyenne en raison de la mortalité naturelle du stock une année donnée en eau douce ou en mer. Cependant, il peut également résulter d’erreurs de reconstitution des remontes, comme une sous-estimation ou une surestimation de la prise totale.






## AJUSTEMENT DES MODÈLES

Les algorithmes MCCM appliqués à l’intégration a posteriori du MBH étaient WinBUGS 1.4.3 et JAGS, et les deux progiciels ont donné des estimations des paramètres pratiquement identiques. Dans la mise en œuvre initiale de WinBUGS, le rodage a été réalisé en environ 10 000 itérations et des fonctions de densité a posteriori bien prononcées ont été obtenues pour les estimations des paramètres. Cependant, avec les deux progiciels, pour certains stocks, les chaînes MCCM pouvaient très rarement s’écarter jusqu’à des valeurs extrêmement faibles pour le paramètre $\beta$ de Ricker ou à des valeurs extrêmement élevées pour le paramètre $a$ de Ricker. Les valeurs extrêmement faibles du paramètre $\beta$ de Ricker vont jusqu’à des valeurs extrêmement élevées, par exemple dix fois la valeur du mode a posteriori, pour des paramètres dérivés comme l’abondance moyenne non exploitée des géniteurs, $S_0$, ou l’abondance du stock reproducteur associée au rendement maximal durable, $S_{rmd}$. De telles valeurs aberrantes extrêmes ont été considérées comme bien en dehors du soutien des données et peuvent être des artefacts du fonctionnement des algorithmes MCCM appliqués.


Pour éviter l’inclusion de valeurs aberrantes extrêmes, une borne minimale a été appliquée à la valeur a priori du paramètre $\beta$ de Ricker. La valeur minimale a priori du paramètre $\beta$ de Ricker a été établie comme suit. Une borne supérieure de la valeur de $S_\textrm{max}$  a été calculée pour chaque stock, soit cinq fois la tendance centrale a priori spécifiée pour $S_\textrm{max}$ : 


\begin{equation}
  S_{\textrm{max},\textrm{max},s} = 5 \times S_{\textrm{max},s} \textrm{ and } \beta_{\textrm{min},s}=\frac{1}{S_{\textrm{max},\textrm{max},s}}. 
\end{equation}

La valeur a priori ajustée pour $\beta_s$ qui a été appliquée était donc :

\begin{equation}
  \textrm{max}\left(\beta_s \sim \ \ln \textrm{Normal}\left(\mu_{\beta,s},\ \ \tau_{\beta,s}\right),\ \beta_{\textrm{min},s}\right)
\end{equation}

L’application de cette valeur a priori modifiée pour $\beta_s$ a ainsi empêché des valeurs anormalement faibles de $\beta_s$ et des valeurs MCCM anormalement grandes pour les points de référence fondés sur l’abondance tels que $S_\textrm{max}$ , $S_\textrm{rmd}$, and $S_0$.

La distribution prédictive a posteriori du paramètre a de Ricker pour une population non échantillonnée, a_p, est donnée par la formule qui suit :


\begin{equation}
  a_p \sim\  \ln \textrm{Normal}\left(\mu_a,\ \tau_a\right)
  (\#eq:unsamp)
\end{equation}
  

Cette distribution reflète la fonction de densité a priori effective pour le paramètre $a$ de Ricker qui a été appliquée pour estimer ce paramètre pour chaque stock.

Afin de fournir des approximations de la façon dont la productivité pourrait varier de façon systématique au fil des ans, nous avons obtenu des représentations de la productivité variable dans le temps en ajoutant les moyennes mobiles $n = 4$ ou 5 ans des effets annuels communs au paramètre $a$ pour chaque stock :

\begin{equation}
  a_{s,y,n}=a_s+\frac{1}{n}\cdot\sum_{i=y-n+1}^{y}T_i
  (\#eq:timevarprod)
\end{equation}


Les estimations finales des distributions a posteriori ont été dérivées dans JAGS en exécutant six chaînes indépendantes avec des points de départ différents pour 100 000 itérations MCCM après un rodage de 20 000. Les échantillons a posteriori ont été éclaircis en conservant un échantillon sur dix afin de réduire l’autocorrélation dans les paramètres fondamentaux et dérivés. La convergence a été évaluée au moyen d’une combinaison de tracés diagnostiques (p. ex. graphiques des traces, distributions a posteriori et tracés Gelman-Rubin-Brooks) et de critères comme le facteur de réduction d’échelle potentiel de Rhat, Gelman et Rubin [@GelmanRubin1992], y compris la version multivariée [@BrooksGelman1998], et le diagnostic de Geweke [@Geweke1992]. Dans tous les cas, les tracés ont montré de bons échantillonnages à partir de la valeur a posteriori avec peu ou pas d’autocorrélation et indiqué que tous les critères de diagnostic se situaient dans des fourchettes généralement associées à la convergence (c. à d. Rhat < 1,05, Gelman-Rubin dans la fourchette [0,99; 1,01] et Geweke dans la fourchette [-2; 2]).





## Sensitivity Analyses {#app:HBMFits-2}

Some additional model runs were implemented to evaluate some different features of the HBM.  See Table \@ref(tab:SensitivityRuns) for brief descriptions of these additional model runs. We term the model run using above described specifications for the HBM the ''base case''.  Note that the results reported below were obtained from earlier WinBUGS 1.4.3 code versions of the HBM which included a simpler approximation for computing $S_\textrm{MSY}$ [i.e., from Table 7.2 of @HilbornWalters1992] than was used in the main body of the report.  The results from these additional runs are summarized further below.   


  
<!-- TABLE C.2. Sensitivity Analyses -->
```{r SensitivityRuns, echo=FALSE, results='asis'}
cap <- "Description of sensitivity runs to evalute the sensitivity of estimation results to model structure and some key inputs."

data.frame(
  `Run` = c(seq(1,6), "7-24", "25", "26"), 
  Description = c(
    "HBM base case but including Korman and English’s (2013) coding in computing precision in the likelihood function from $\\sigma$",
    "Same as HBM base case but with no prior lower bounds on $\\beta$.",
    "Same as HBM base case but leaving out common shared year effects.",
    "Non-hierarchical model run with no common shared year effect but including the same  $S_\\textrm{max}$ prior information as in the base case HBM.",
    "Same as HBM base case but normal priors on  $S_\\textrm{max}$ instead of the base case lognormal prior on Ricker $\\beta$.",
    "Same as HBM base case but with vague Ricker $\\beta$ priors, but including the prior lower bound on Ricker $\\beta$.",
    "Leave out stock-recruit data in the HBM, one stock at a time.",
    "Leave out stock-recruit data for the Babine Enhanced stocks in the HBM (i.e., Pinkut and Fulton).",
    "Same as HBM base case but leave out Babine Enhanced stocks (i.e., Pinkut and Fulton) and apply vague  $S_\\textrm{max}$ priors to Bear, Kitwanga, and Sustut."
  ),
  check.names = FALSE
) %>%
  csas_table(
    format = "latex", 
    escape = FALSE, 
    font_size = 10, 
    # align = c("p{1.2cm}","p{12cm}"),
    align = c("l", "l"),
    caption = cap, #paste("(tab:SensitivityRuns)", cap)
  ) %>%
  kableExtra::row_spec(seq(1,8), hline_after = TRUE) %>%
  kableExtra::column_spec(2, width = "12cm")
```


## Results

### Shrinkage in the Ricker $a$ Parameter in Going From a Non-HBM to an HBM  {#HBMShrinkage}

```{r, echo=FALSE}
shrink <- (HBM.results$Shrinkage$Shrinkage * 100) %>% range() %>% round
kitwanga <- round((HBM.results$Shrinkage %>% filter(Stock == "Kitwanga") %>% select(Shrinkage) %>% unlist)*100 )
pinkut <- round((HBM.results$Shrinkage %>% filter(Stock == "Pinkut") %>% select(Shrinkage) %>% unlist)*100 )
fulton <- round((HBM.results$Shrinkage %>% filter(Stock == "Fulton") %>% select(Shrinkage) %>% unlist)*100 )
other <- HBM.results$Shrinkage %>% filter(Stock %in% c("Kitwanga", "Pinkut", "Fulton" == FALSE)) %>% select(Shrinkage) %>% unlist %>% range
other <-round(other*100,1)
sig.sd <- (HBM.results$Shrinkage$`Diff.SD` * -100) %>% range() %>% round(digits = 1)  # % reduction
```

In both the non-HBM and HBM models a common shared year effect was estimated to make the shrinkage analysis valid.  Under the non-HBM the prior for the Ricker $a$ parameter for each stock was similarly lognormal, had $a$ prior median of $\log(0.5)$ and precision of 1.  Compared to the non-HBM a moderate amount of shrinkage can be seen seen for the HBM estimates (Figure \@ref(fig:HBMShrinkage)). For example the Asitka stock which had the highest posterior median value for the Ricker $a$ parameter under both models showed a `r -shrink[1]`% decrease in the Ricker $a$ parameter (Table \@ref(tab:HBMShrinkageVal)).  This was the largest percentage decrease among the Skeena Sockeye salmon stocks included in the HBM.  In contrast the Kitwanga stock which had the second lowest posterior median for the Ricker $a$ parameter under the non-HBM showed the largest increase of `r kitwanga`% when going from the non-HBM to the HBM.  In contrast the Pinkut and Fulton stocks which had posterior medians for Ricker $a$ under the non-HBM close to the middle range of the Posterior median estimates showed very little shrinkage, i.e., `r pinkut`% and `r fulton`%, respectively (Figure \@ref(fig:HBMShrinkage), Table \@ref(tab:HBMShrinkageVal)).  For all of the 18 Skeena Sockeye salmon stocks the posterior standard deviation (SD) for Ricker $a$ parameter estimates were all smaller, i.e., `r sig.sd[1]`% to `r sig.sd[2]`% smaller, under the HBM than under the non-HBM (Table \@ref(tab:HBMShrinkageVal)).


<!-- Figure C.1. Shrinkage Plot -->
```{r, echo=FALSE}
cap <- "Shrinkage plot for posterior median values for the Ricker $a$ parameter obtained under non-HBM and HBM models of stock-recruit data for 18 Skeena River Sockeye salmon stocks."
```
```{r HBMShrinkage, echo=FALSE, fig.width=7, fig.cap=cap}
HBM.results$Shrinkage %>%
  select(Stock, ends_with("median")) %>%
  gather(key=Model, value = Median, ends_with("median")) %>%
  mutate(
    Model = str_replace(Model, "[\\.[:space:]]median", "") %>% factor(levels = c("nonHBM", "HBM"))
  ) %>%
  ggplot(., aes(x=Model, y = Median)) +
  geom_point(aes(color = Stock)) +
  geom_line(aes(group = Stock, color = Stock)) +
  theme_classic(14) +
  theme(legend.title = element_blank()) +
  labs(
    y = "Posterior Median"
  )
```

<!-- TABLE C.3. Ricker a shrinkage -->
```{r HBMShrinkageVal, echo=FALSE, results='asis'}
cap <- "Posterior median estimates and standard deviations (SD) for the Ricker $a$ parameter for the 18 Skeena River Sockeye salmon stocks under non-HBM and HBM models  The percentage change shows the percentage change in the parameter estimate in going from the non-HBM to the HBM implementation.  "

HBM.results[['Shrinkage']] %>%
  mutate(
    nonHBM.median = round(nonHBM.median, 3),
    HBM.median= round(HBM.median, 3),
    nonHBM.SD = round(nonHBM.SD, 3),
    HBM.SD = round(HBM.SD, 3),
    Shrinkage = paste0(round(Shrinkage * 100,1), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100,1), "\\%")
  ) %>%
  rename(
    `nonHBM Median` = nonHBM.median,
    `HBM Median` = HBM.median,
    `nonHBM SD` = nonHBM.SD,
    `HBM SD` = HBM.SD,
    `SD \\% Diff` = Diff.SD,
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap #paste("(ref:tabSenRun1)", cap)
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

### Common Shared Year Effect

The common shared year effects represent average deviations from Ricker model stock-productivity predictions across stocks in a given year (Figure \@ref(fig:HBMYrEff)). Estimates varied from year to year with many years being close to the Ricker model predictions, while other years showing notable positive and negative deviations The 1994 common shared year effect represented the largest deviation from Ricker stock-productivity predictions, with a strong reduction in productivity. The 4-year and 5-year rolling means provide smoothed representations of estimated common shared year effects within four and five year blocks and make it easier to visualize potential common shared trends in stock productivity than plots of annual estimates.  The common shared year effects derive from the average of stock productivity deviates across the stocks where stock-recruit data are available in a given year and acquire credibility through commonality in annual productivity deviates across several of the stocks.  In contrast, Kalman filter representations of time varying productivity rely on apparent time series of deviates from Ricker-model predictions of long-term average productivity based on data from a single stock.  The Kalman filter approach does not allow any potential statistical representation of common patterns in productivity deviates between stocks in larger watershed. Also in contrast to the common-shared year effect approach the Kalman filter approach cannot be applied to stock-recruit data time series where there are one or more missing years of data within a time series.

<!-- FIGURE C.2. Common Shared Year Effect -->
```{r, echo=FALSE}
cap <- "Estimated common shared year effect shared across the 18 Skeena stocks with a 4-year rolling mean (A) and a 5-year rolling mean (B) overlaid. Points indicate mean with error bars indicating the 95\\% credible intervals, while line and shading indicates the mean and 95\\% credible intervals for the rolling mean."
```
```{r HBMYrEff, fig.width=7.5, fig.cap=cap}
include_graphics("data/HBM/Appendix-HBM-common_year_eff.pdf")
```

While these yearly deviations, whether from common shared year effects or Kalman filter, could represent improved or diminished survival in the fresh or saltwater system, they could also represent an under or overestimation in total catch, and there is currently no way to distinguish between authentic shared survival rate effects and run reconstruction error effects. As such, negative or positive year effects cannot be directly attributed to either an environmental or run reconstruction effect as the two will be confounded. 

As such, time varying productivity should be viewed as a method to improve model fitting, but does not provide objective criteria that can be used to set or judge management responses.   For example, where there were runs of strongly positive or negative common shared year effects in recent years, this could reflect either runs of either high or low stock productivity shared between stocks.  Alternatively, it could reflect a run of years in which fishery catches for all or most stocks were systematically under-reported or over-reported.  If the latter hypothesis were correct, then any adjustments to harvest control rules, e.g., adjustments to escapement targets, to attempt to respond to apparent productivity changes, could have unintended consequences in achieving fishery and salmon population conservation objectives.

To evaluate the sensitivity of reference points to estimated changes in productivity, high and low productivity periods were identified and the posterior predictive distributions for $S_{msy}$ and \Umsy were computed based on the common shared year effects in these blocks of years based on estimates of time varying productivity by stock (see equation \@ref(eq:timevarprod)).  The years showing the largest mostly positive common shared year effects included 1980-1992 (Fig. \@ref(fig:HBMYrEff)).  The years showing the lowest mostly negative common shared year effects included 1999-2014 (Fig. \@ref(fig:HBMYrEff)).  $S_{msy}$ and \Umsy estimates were significantly lower in the latter block of years with the posterior means for \Smsy and also \Umsy ranging between 21% and 50% lower than those estimates in the high productivity period from 1980-1992 (Tables \@ref(tab:SmsyProd) and \@ref(tab:UmsyProd)).  The 95% credible intervals for the percentage differences for both \Smsy and \Umsy included only negative values (Tables \@ref(tab:SmsyProd) and \@ref(tab:UmsyProd)).  These results suggest that systematic reductions in stock productivity could result in estimates of both \Umsy and \Smsy being lowered.  Should \Smsy be used in forming escapement targets and reference points for fishery management and conservation, lowered productivity could result in lower escapement targets.  Because the \Umsy estimates are highly correlated with the \Smsy estimates, the \Umsy estimates could also be expected to decrease with decreases in \Smsy estimates and it would be appropriate also to reduce harvest rates to accommodate lowered productivity.  However, if only changes in estimates of \Smsy were considered in responses to apparent changes in stock productivity and reductions in harvest rates were not implemented, this could also lead to unintended consequences in meeting stock conservation and fishery objectives.

<!-- TABLE C.4. Smsy in high/low years -->
```{r SmsyProd, echo=FALSE}
cap <- "Comparison of stock-specific $S_\\textrm{MSY}$ in high (i.e., 1980-1992) and low (i.e., 1999-2014) periods of productivity and the percentage differnce between periods."

HBM.results[['Smsy Productivity']] %>%
  mutate(
    High = round(High),
    Low = round(Low),
    Diff      = ifelse(is.na(Diff), NA, paste0(round(Diff*100), "\\%")),
    Diff_2.5  = ifelse(is.na(Diff), NA, paste0(round(Diff_2.5*100), "\\%")),
    Diff_97.5 = ifelse(is.na(Diff), NA, paste0(round(Diff_97.5*100), "\\%"))
  ) %>%
  # select(Low, High, Diff, Diff_2.5, Diff_97.5) %>%
  rename(
    `High` = High,
    `Low` = Low,
    `\\% Diff` = Diff,
    `Lower CI` = Diff_2.5,
    `Upper CI` =Diff_97.5
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 5)),
    caption = cap #paste("(ref:tabSenRun1)", cap)
  ) %>%
  kableExtra::column_spec(2:5, width = "1.5cm")
```

\clearpage
<!-- TABLE C.5. Umsy in high/low years -->
```{r UmsyProd, echo=FALSE}
cap <- "Comparison of stock-specific $U_\\textrm{MSY}$ in high (i.e., 1980-1992) and low (i.e., 1999-2014) periods of productivity and the percentage differnce between periods."

HBM.results[['Umsy Productivity']] %>%
  mutate(
    High = round(High),
    Low = round(Low),
    Diff      = ifelse(is.na(Diff), NA, paste0(round(Diff*100), "\\%")),
    Diff_2.5  = ifelse(is.na(Diff), NA, paste0(round(Diff_2.5*100), "\\%")),
    Diff_97.5 = ifelse(is.na(Diff), NA, paste0(round(Diff_97.5*100), "\\%"))
  ) %>%
  # select(Low, High, Diff, Diff_2.5, Diff_97.5) %>%
  rename(
    `High` = High,
    `Low` = Low,
    `\\% Diff` = Diff,
    `Lower CI` = Diff_2.5,
    `Upper CI` =Diff_97.5
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 5)),
    caption = cap #paste("(ref:tabSenRun1)", cap)
  ) %>%
  kableExtra::column_spec(2:5, width = "1.5cm")
```

\newpage
### Sensitivity Run 1:  Effect of Korman and English’s (2013) Coding Error for their HBM {#app:HBMFits-2-1}
```{r, echo=FALSE}
sig.mean <- (HBM.results$`Run 1`$Diff.mean * 100) %>% range() %>% round
sig.sd <- (HBM.results$`Run 1`$Diff.SD * 100) %>% range() %>% round
```


There was a coding error in the model used by @KormanEnglish2013; their code incorrectly transformed the parameter $\sigma_i$ to $\tau_i$ using the incorrect code:  \texttt{tau[i]<-pow(sd[i],-0.5)} which instead should have been \texttt{tau[i]<-pow(sd[i],-2)}. This coding error changed very little the HBM posterior results for the Ricker $a$ and $\beta$ parameters for the 18 stocks (Table \@ref(tab:SenRun1)).  However, the estimates of the $\sigma_i$ parameter were between `r sig.mean[1]`% and `r sig.mean[2]`%  of those obtained under the HBM base case.   The posterior SDs for $\sigma_i$ ranged between `r sig.sd[1]`% and `r sig.sd[2]`%  larger than those obtained under the base case.  Either the lower or upper boundary point on the prior for $\sigma_i$ was hit for some of the stocks.    If the coding error had persisted, any simulations of stock-recruit data using the estimated values for $\sigma_i$ may have led to results with excessive variability.  It is thus essential for this coding error to be corrected in any further implementations of Korman and English’s (2013) HBM.

<!-- TABLE C.6 Sensitivity Run 1 -->
```{r SenRun1, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $\\sigma$ from the base case (coding error removed) and model run that included Korman and English’s (2013) coding error."

HBM.results[['Run 1']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    Code.Error.mean = round(Code.Error.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    Code.Error.SD = round(Code.Error.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100), "\\%")
  ) %>%
  rename(
    `Base Case mean $\\sigma$` = Base.Case.mean,
    `Code Error mean $\\sigma$` = Code.Error.mean,
    `\\% Diff` = Diff.mean,
    `Base Case SD($\\sigma$)` = Base.Case.SD,
    `Code Error SD($\\sigma$)` = Code.Error.SD,
    `\\% Diff ` = Diff.SD,
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap #paste("(ref:tabSenRun1)", cap)
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```



\clearpage
### Sensitivity Run 2:  Same as HBM Base Case But With No Prior Lower Bound on the Ricker $\beta$ Parameter



When there was no prior lower bound included the Ricker $\beta$ parameter by stock, the estimates of $S_\textrm{max}$ and MSY-based reference points included some extremely high MCMC chain values that were way out in the tails of the Markov chains and very far removed from the range of values with support from the data; for these stocks, posterior means, medians, and probability interval values were highly sensitive to the inclusion of these extreme outlier values in the chains (see Table \@ref(tab:SenRun2) for some example results for $S_\textrm{MSY}$).  It is common in implementations of MCMC implementations such as WinBUGS to set bounds on key variables in the model to prevent extreme outlier values in the chains from affecting the posterior calculations [e.g., @MeyerMillar1999; @MichielsensMcAllister2004].  It is thus recommended that prior lower bounds on the Ricker $\beta$ parameter be implemented for each stock to eliminate this source of bias.

The $U_\textrm{MSY}$ estimates from the HBM were relatively insensitive to lifting the prior maximum bound on $S_\textrm{max}$ (Table \@ref(tab:SenRun2Umsy)).   While posterior means differed by less than a few percent for all stocks, posterior standard deviation values were up to 13\% larger when the prior maximum bound on \Smax was lifted.  


<!-- TABLE C.7 Sensitivity Run 2 -->
```{r SenRun2, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$  from the HBM base case and model run where no prior upper bounds were placed on \\Smax."

HBM.results[['Run 2 Smsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    No.Bound.mean = round(No.Bound.mean),
    Base.Case.SD = round(Base.Case.SD),
    No.Bound.SD = round(No.Bound.SD),
    Diff.mean = paste0(round(Diff.mean*100,1), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 1), "\\%")
  ) %>%
  rename(
    `Base Case mean $S_\\textrm{MSY}$` = Base.Case.mean,
    `No Bound mean $S_\\textrm{MSY}$` = No.Bound.mean,
    `\\% Diff` = Diff.mean,
    `Base Case SD($S_\\textrm{MSY}$)` = Base.Case.SD,
    `No Bound SD($S_\\textrm{MSY}$)` = No.Bound.SD,
    `\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap, #paste("(ref:tabSenRun2)", cap)
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

<!-- TABLE C.8 Sensitivity Run 2 -->
```{r SenRun2Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the HBM base case and model run where no prior upper bounds were placed on \\Smax."

HBM.results[['Run 2 Umsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean,3),
    No.Bound.mean = round(No.Bound.mean,3),
    Base.Case.SD = round(Base.Case.SD,3),
    No.Bound.SD = round(No.Bound.SD,3),
    Diff.mean = paste0(round(Diff.mean*100,1), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 1), "\\%")
  ) %>%
  rename(
    `Base Case mean $U_\\textrm{MSY}$` = Base.Case.mean,
    `No Bound mean $U_\\textrm{MSY}$` = No.Bound.mean,
    `\\% Diff` = Diff.mean,
    `Base Case SD($U_\\textrm{MSY}$)` = Base.Case.SD,
    `No Bound SD($U_\\textrm{MSY}$)` = No.Bound.SD,
    `\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap, #paste("(ref:tabSenRun2)", cap)
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
### Sensitivity Run 3: Same as HBM Base Case But Leaving Out Common Shared Year Effects

```{r, echo=FALSE}
sig.mean <- (HBM.results[['Run 3 Smsy']]$Diff.mean * 100)  %>% range() %>% round
sig.sd <- (HBM.results[['Run 3 Smsy']]$Diff.SD * 100) %>% range()  %>% round
```

Significant, strong common shared year effects were estimated for numerous years in the 1960-2014 brood year time series.  Separating out this effect provided more precise estimates of Ricker stock recruit parameters for several of the stocks and more precise estimates of management quantities of interest.  This also allowed for common shared systematic change in stock productivity to be estimated.  The posterior means for the Smsy reference point by stock for example were between about `r sig.mean[1]`% and `r sig.mean[2]`% different between runs when common shared year effects were excluded versus accounted for (Table \@ref(tab:SenRun3)).  When no common shared year effect was included in the HBM, estimates of Ricker stock-recruit parameters and associated management parameters for several of the stocks were on average less precisely estimated with posterior SDs being up to about `r sig.sd[2]`% larger for $S_\textrm{msy}$ for several of the stocks.

The $U_\textrm{MSY}$ estimates from the HBM were relatively insensitive to removing common shared year effects from the HBM (Table \@ref(tab:SenRun3Umsy)).  

<!-- TABLE C.9 Sensitivity Run 3 -->
```{r SenRun3, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$ from the HBM base case and model run where no prior upper bounds were placed on \\Smax."

HBM.results[['Run 3 Smsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    No.TE.mean = round(No.TE.mean),
    Base.Case.SD = round(Base.Case.SD),
    No.TE.SD = round(No.TE.SD),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $S_\\textrm{MSY}$` = Base.Case.mean,
  	`No \\newline $T_y$ \\newline mean $S_\\textrm{MSY}$` = No.TE.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($S_\\textrm{MSY}$)` = Base.Case.SD,
  	`No \\newline $T_y$ \\newline SD($S_\\textrm{MSY}$)` = No.TE.SD,
  	`\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap #paste("(ref:tabSenRun3)", cap)
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

<!-- Table C.10 Sensitivity Run 3 -->
```{r SenRun3Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the HBM base case and model run where no prior upper bounds were placed on \\Smax."

HBM.results[['Run 3 Umsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    No.TE.mean = round(No.TE.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    No.TE.SD = round(No.TE.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $U_\\textrm{MSY}$` = Base.Case.mean,
  	`No \\newline $T_y$ \\newline mean $U_\\textrm{MSY}$` = No.TE.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($U_\\textrm{MSY}$)` = Base.Case.SD,
  	`No \\newline $T_y$ \\newline SD($U_\\textrm{MSY}$)` = No.TE.SD,
  	`\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap #paste("(ref:tabSenRun3)", cap)
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
### Sensitivity Run 4: Non-Hierarchical Model Run With No Common Shared Year Effect But Including the Same $S_\textrm{max}$ Prior Information As in the Base Case HBM

```{r, echo=FALSE}
sig.mean <- (HBM.results[['Run 4 Smsy']]$Diff.mean * 100) %>% range()  %>% round
sig.sd <- (HBM.results[['Run 4 Smsy']]$Diff.SD * 100) %>% range()  %>% round

smsy.diff <- filter(HBM.results[['Run 4 Smsy']], Stock == "Sum Smsy across stocks") %>% select(Diff.mean, Diff.SD) %>% unlist * 100 %>% round

umsy.diff <- HBM.results[['Run 4 Umsy']] %>% select(Diff.SD) %>% unlist %>% max
umsy.diff <- round(umsy.diff*100)
```


When a nonhierarchical Bayesian model(nonHBM) with no common shared year effects was run, estimates of Ricker stock-recruit parameters and associated management parameters for several of the stocks were on average less precisely estimated with posterior SD in Smsy for example on average being about `r sig.sd[1]`% to `r sig.sd[2]`% different between the nonHBM and HBM runs (Table \@ref(tab:SenRun4)).  Percentage differences between the nonHBM and HBM for posterior mean estimates for Smsy parameters ranged by stock between `r sig.mean[1]`% and `r sig.mean[2]`%.  These results indicate that on average Ricker and msy-based parameter estimates are more precisely estimated with the HBM and results for some quantities for some stocks can differ considerably.  However, the sum of the $S_\textrm{MSY}$ estimates across stocks was only about `r round(smsy.diff['Diff.mean'])`% larger under the non-hierarchical model but the posterior SD in the $S_\textrm{MSY}$ values summed over the Skeena River stocks was `r round(smsy.diff['Diff.SD'])`% larger than that for the HBM (Table \@ref(tab:SenRun4)).

The posterior means for  $U_\textrm{MSY}$ were relatively insensitive to fitting a nonHBM, but the posterior SDs for $U_\textrm{MSY}$ mostly increased by up to `r umsy.diff`% larger than those under the HBM  (Table \@ref(tab:SenRun4Umsy)).  

<!-- TABLE C.11 - Sensitivity Run 4 -->
```{r SenRun4, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$ from the base case HBM and nonHBM run."

HBM.results[['Run 4 Smsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    nonHBM.mean = round(nonHBM.mean),
    Base.Case.SD = round(Base.Case.SD),
    nonHBM.SD = round(nonHBM.SD),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $S_\\textrm{MSY}$` = Base.Case.mean,
  	`nonHBM \\newline mean $S_\\textrm{MSY}$` = nonHBM.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($S_\\textrm{MSY}$)` = Base.Case.SD,
  	`nonHBM \\newline SD($S_\\textrm{MSY}$)` = nonHBM.SD,
  	`\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

<!-- TABLE C.12 - Sensitivity Run 4 -->
```{r SenRun4Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the base case HBM and nonHBM run."

HBM.results[['Run 4 Umsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    nonHBM.mean = round(nonHBM.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    nonHBM.SD = round(nonHBM.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $U_\\textrm{MSY}$` = Base.Case.mean,
  	`nonHBM \\newline mean $U_\\textrm{MSY}$` = nonHBM.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($U_\\textrm{MSY}$)` = Base.Case.SD,
  	`nonHBM \\newline SD($U_\\textrm{MSY}$)` = nonHBM.SD,
  	`\\% Diff ` = Diff.SD
  ) %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
### Sensitivity Run 5: Normal Priors on Smax in the HBM Instead of the Lognormal Prior on Ricker $\beta$

```{r, echo=FALSE}
sig.mean <- (HBM.results[['Run 5 Smsy']]$Diff.mean * 100) %>% range()  %>% round
sig.sd <- (HBM.results[['Run 5 Smsy']]$Diff.SD * 100) %>% range()  %>% round
```

When a normal prior for $S_\textrm{max}$ was applied instead of a lognormal prior on the Ricker $\beta$ parameter in the HBM, but otherwise using the same input information from the lake productivity analyses, the posterior estimates for several of the quantities became less precise and posterior estimates differed markedly for some of the quantities.  Posterior SDs for $S_\textrm{MSY}$ were for example much larger on average, e.g., between about `r sig.sd[1]`% and `r sig.sd[2]`% larger (Table \@ref(tab:SenRun5)).  Posterior mean estimates for $S_\textrm{MSY}$ differed between the two model runs by `r sig.mean[1]`% to `r sig.mean[2]`%.  Though it appears the same information is used in a normal prior for $S_\textrm{max}$, this prior on average loses information about the Ricker $\beta$ parameter compared to a prior for the Ricker $\beta$ parameter that uses the same $S_\textrm{max}$ information. 

The $U_\textrm{MSY}$ estimates from the HBM were relatively insensitive to replacing the lognormal prior for the Ricker $\beta$ parameter with a normal prior for  $S_\textrm{max}$ (Table \@ref(tab:SenRun5Umsy)). 

<!-- TABLE C.13 - Sensitivity Run 5 -->
```{r SenRun5, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$ from the HBM base case and model run with a Normal priors on $S_\\textrm{max}$."

HBM.results[['Run 5 Smsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    Normal.Prior.mean = round(Normal.Prior.mean),
    Base.Case.SD = round(Base.Case.SD),
    Normal.Prior.SD = round(Normal.Prior.SD),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $S_\\textrm{MSY}$` = Base.Case.mean,
  	`Normal Prior mean $S_\\textrm{MSY}$` = Normal.Prior.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($S_\\textrm{MSY}$)` = Base.Case.SD,
  	`Normal Prior SD($S_\\textrm{MSY}$)` = Normal.Prior.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
<!-- TABLE C.14 - Sensitivity Run 5 -->
```{r SenRun5Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the HBM base case and model run with a Normal priors on $S_\\textrm{max}$."

HBM.results[['Run 5 Umsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    Normal.Prior.mean = round(Normal.Prior.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    Normal.Prior.SD = round(Normal.Prior.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $U_\\textrm{MSY}$` = Base.Case.mean,
  	`Normal Prior mean $U_\\textrm{MSY}$` = Normal.Prior.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($U_\\textrm{MSY}$)` = Base.Case.SD,
  	`Normal Prior SD($U_\\textrm{MSY}$)` = Normal.Prior.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
### Sensitivity Run 6: Application of Vague Ricker $\beta$ Priors in the HBM, but Including the Prior Lower Bound on $\beta$
```{r, echo=FALSE}
sig.mean <- (HBM.results[['Run 6 Smsy']]$Diff.mean * 100) %>% range() %>% round
sig.sd <- (HBM.results[['Run 6 Smsy']]$Diff.SD * 100) %>% range() %>% round

umsy.diff <- HBM.results[['Run 6 Umsy']] %>% select(Diff.mean) %>% unlist %>% max
umsy.diff <- round(umsy.diff*100)
```

When a vague prior was applied for the Ricker $\beta$ prior for all 18 Skeena Sockeye salmon stocks in the HBM, posterior estimates for the abundance-based management quantities were less precise on average with posterior SDs, e.g., for \Smsy ranging between `r sig.sd[1]`% to `r sig.sd[2]`% larger under the vague priors (Table \@ref(tab:SenRun6)).  Posterior means for $S_\textrm{MSY}$ estimates in the HBM that used vague priors for the Ricker $\beta$ parameter were between about `r sig.mean[1]`% and `r sig.mean[2]`% different from those obtained under the mixture of informed and vague priors in the base case HBM.  The use of informative priors for the Ricker $\beta$ parameter based on prior information on $S_\textrm{max}$ via the lake productivity analyses thus combined with the data to provide more precise stock-recruit parameter estimates that in some cases differed from the less precise estimates given by the stock-recruit data.  


The $U_\textrm{MSY}$ estimates from the HBM were relatively insensitive to prior for all Ricker $\beta$ parameter vague priors though for a few of the stocks the posterior means were up to `r umsy.diff`% larger (Table \@ref(tab:SenRun6Umsy)). 

<!-- TABLE C.15 - Sensitivity Run 6 -->
```{r SenRun6, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$ from the HBM base case and model run with a Normal priors on $S_\\textrm{max}$."

HBM.results[['Run 6 Smsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    Vague.Prior.mean = round(Vague.Prior.mean),
    Base.Case.SD = round(Base.Case.SD),
    Vague.Prior.SD = round(Vague.Prior.SD),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $S_\\textrm{MSY}$` = Base.Case.mean,
  	`Vague $\\beta$ Prior mean $S_\\textrm{MSY}$` = Vague.Prior.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($S_\\textrm{MSY}$)` = Base.Case.SD,
  	`Vague $\\beta$ Prior SD($S_\\textrm{MSY}$)` = Vague.Prior.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

<!-- TABLE C.16 - Sensitivity Run 6 -->
```{r SenRun6Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the HBM base case and model run with a Normal priors on $S_\\textrm{max}$."

HBM.results[['Run 6 Umsy']] %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    Vague.Prior.mean = round(Vague.Prior.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    Vague.Prior.SD = round(Vague.Prior.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean $U_\\textrm{MSY}$` = Base.Case.mean,
  	`Vague $\\beta$ Prior mean $U_\\textrm{MSY}$` = Vague.Prior.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD($U_\\textrm{MSY}$)` = Base.Case.SD,
  	`Vague $\\beta$ Prior SD($U_\\textrm{MSY}$)` = Vague.Prior.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

\clearpage
### Sensitivity Runs 7-25.  Leave Out Stock-Recruit Data in the HBM, One Stock at a Time

To evaluate the relative influence of each stock-recruit data set from each stock, the HBM was run dropping out the stock-recruit data for one stock at a time.  In run 25 the stock-recruit data for both of the Babine Enhanced stocks (i.e., Fulton and Pinkut) were left out of the HBM.  The posterior predictive distribution for the Ricker $a$ parameter for an “unsampled” stock was computed for each of these runs (see equation \@ref(eq:unsamp)).  The posterior predictive distributions were plotted under each of the HBM runs 7-25 and under the base case HBM shows that the posterior predictive distributions were very similar between all HBM runs 7-25 and the base case HBM run (Figure \@ref(fig:jackProd)).  The posterior mean estimates of the time series of common shared year effects also did not change their sign or markedly change in magnitude when the stock-recruit data from one of the stocks or both of the Babine enhanced stocks were removed from the HBM (Figure \@ref(fig:jackTE)).  These results indicate that no one stock, nor the enhanced Babine Sockeye salmon stocks, had a substantive influence on the HBM results.  Furthermore results indicate that regardless of whether Pinkut and Fulton channel data were included or excluded, very similar among stocks posterior distribution of the Ricker $a$ parameter (Figure \@ref(fig:jackProd)) and shared year-effects on productivity (Figure \@ref(fig:jackTE)) were produced.  

The temporal variation in shared year effect estimates represent the combined effects of potential changes in both freshwater and marine processes (Figure \@ref(fig:jackTE)).  The combined effects of spawning channels on recruits/spawner are clearly similar to those of nearby natural spawning streams (Figure \@ref(fig:jackTE)).  However, by providing more spawning gravel, the channels have increased the total abundance of adult recruits and spawners in the Skeena system (Randall Peterman, pers. comm.).

<!-- Figure C.3 - Sensitivity Run 7-25 -->
```{r, echo=FALSE}
cap <- "Posterior predictive distributions for the Ricker $a$ parameter when the Sockeye salmon stock-recruit data from one stock at a time was dropped from the HBM for the Skeena watershed (runs 7-24) and the stock-recruit data were dropped for both of the Babine Enhanced Sockeye salmon stocks, i.e., both Pinkut and Fulton (run 25). Base case posterior predictive distribution is coloured dark grey, with colours used for runs 7-25."
```
```{r jackProd,   fig.cap=cap}
include_graphics("data/HBM/Appendix-HBM-Productivity-jackknife.pdf")
```

<!-- Figure C.4 - Sensitivity Run 7-25 -->
```{r, echo=FALSE}
cap <- "Posterior mean estimates for the common shared year effect when the Sockeye salmon stock-recruit data from one stock at a time was dropped from the HBM for the Skeena watershed (runs 7-24) and the stock-recruit data were dropped for both of the Babine Enhanced Sockeye salmon stocks, i.e., both Pinkut and Fulton (run 25). Base case posterior predictive distribution is coloured dark grey, with colours used for runs 7-25."
```
```{r jackTE,   fig.cap=cap}
include_graphics("data/HBM/Appendix-HBM-yeareffect-jackknife.pdf")
```



\clearpage
### Sensitivity Run 26: Removal of Enhanced Stocks and Vague Ricker $\beta$ Priors for Select Stocks
```{r, echo=FALSE}
sig.mean <- (HBM.results[['Run 26 Smsy']]$Diff.mean * 100) %>% range() %>% round
sig.sd <- (HBM.results[['Run 26 Smsy']]$Diff.SD * 100) %>% range() %>% round


smsy.diff <- HBM.results[['Run 26 Smsy']] %>% 
  # select(Stock, Diff.mean, Diff.SD) %>% 
  arrange (Diff.mean) %>%
  mutate(Base.Case.CV = round(Base.Case.SD /Base.Case.mean*100)) %>%
   mutate(Run.26.CV = round(Run.26.SD /Run.26.mean*100)) %>%
  mutate(Perc.Diff =  round(Diff.mean*100), Perc.SD =  round(Diff.SD*100)) %>%
  arrange(Stock)
smsy.diff2 <- smsy.diff %>% filter(Stock %in% c("Bear", "Kitwanga", "Sustut"))

umsy.diff <- HBM.results[['Run 26 Umsy']] %>% select(Stock, Diff.mean) %>% 
  arrange (Diff.mean) %>% 
  mutate(Perc =  round(Diff.mean*100)) %>%
  tail(n=2) %>%
  arrange(Stock)
# umsy.diff <- round(umsy.diff*100)
```

For the final sensitivity run (hereafter, 'run 26') the enhanced stocks were removed and vague priors were applied to the Ricker $\beta$ prior for Bear, Kitwanga and Sustut, which were stocks highlighted as stocks of interest when the HBM results were compared to results form single stock models.  Estimates of the posterior mean for the abundance-based management quantity \Smsy were generally similar to the base case (i.e., less than 10% change) for stocks where the \Smax prior was not changed relative to the base case. The exception was Babine Late Wild, which had a `r filter(smsy.diff, Stock %in% c("Babine Late Wild"))$Perc.Diff`% reduction in the \Smsy estimate, however Babine Late Wild also had the highest posterior SD estimate of all stocks with a CV of `r filter(smsy.diff, Stock %in% c("Babine Late Wild"))$Base.Case.CV`% and `r filter(smsy.diff, Stock %in% c("Babine Late Wild"))$Run.26.CV`% for  base case and run 26 respectively. For Bear, Kitwanga, and Sustut applying a vague prior resulted in declines in the posterior mean of \Smsy  from `r max(smsy.diff2$Perc.Diff)`% to `r min(smsy.diff2$Perc.Diff)`% relative to the base case. Precision in \Smsy estimates varied from stock to stock ranging from a `r -sig.sd[1]`% reduction in the posterior SD to an increase of  `r sig.sd[2]`% relative to the base case (Table \@ref(tab:SenRun26)). For Bear, and Sustut the posterior SD was reduced (`r pasteList(-filter(smsy.diff, Stock %in% c("Bear", "Sustut"))$Perc.SD, "\\%")` respectively), while for Kitwanga the Posterior SD was increased by `r filter(smsy.diff, Stock %in% c("Kitwanga"))$Perc.SD`%. For stocks where changes were not applied to the \Smax  prior changes to the posterior SD ranged from  `r filter(smsy.diff, Stock %in% c("Bear", "Sustut", "Kitwanga") == FALSE)$Perc.SD %>% min`% to `r filter(smsy.diff, Stock %in% c("Bear", "Sustut", "Kitwanga") == FALSE)$Perc.SD %>% max`%.


The \Umsy posterior estimates  were relatively insensitive to these changes implemented in run 26 (i.e., under 10% change in the posterior mean), the exceptions were `r pasteList(umsy.diff$Stock[1:2])` which had posterior means that were   `r pasteList(umsy.diff$Perc[1:2], "\\%")` larger (Table \@ref(tab:SenRun26Umsy)). 

<!-- TABLE C.17 - Sensitivity Run 26 -->
```{r SenRun26, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $S_\\textrm{MSY}$ from the HBM base case and model run where enhanced stocks were removed and vague $S_\\textrm{max}$ priors  were used for Bear, Kitwanga, and Sustut."

HBM.results[['Run 26 Smsy']] %>%
  filter(Stock %in% c("Pinkut","Fulton") == FALSE) %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean),
    Run.26.mean = round(Run.26.mean),
    Base.Case.SD = round(Base.Case.SD),
    Run.26.SD = round(Run.26.SD),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean \\Smsy` = Base.Case.mean,
  	`Run 26 mean \\Smsy` = Run.26.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD(\\Smsy)` = Base.Case.SD,
  	`Run 26 SD(\\Smsy)` = Run.26.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::row_spec(18, hline_after = TRUE) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```

<!-- TABLE C.18 - Sensitivity Run 26 -->
```{r SenRun26Umsy, echo=FALSE, results='asis'}
cap <- "Posterior means and posterior standard deviations for $U_\\textrm{MSY}$ from the HBM base case and model run where enhanced stocks were removed and vague  $S_\\textrm{max}$ priors were used for Bear, Kitwanga, and Sustut."

HBM.results[['Run 26 Umsy']] %>%
  filter(Stock %in% c("Pinkut","Fulton") == FALSE) %>%
  mutate(
    Base.Case.mean = round(Base.Case.mean, 3),
    Run.26.mean = round(Run.26.mean, 3),
    Base.Case.SD = round(Base.Case.SD, 3),
    Run.26.SD = round(Run.26.SD, 3),
    Diff.mean = paste0(round(Diff.mean*100,0), "\\%"),
    Diff.SD = paste0(round(Diff.SD * 100, 0), "\\%")
  ) %>%
  rename(
  	`Base Case mean \\Umsy` = Base.Case.mean,
  	`Run 26 mean \\Umsy` = Run.26.mean,
  	`\\% Diff` = Diff.mean,
  	`Base Case SD(\\Umsy)` = Base.Case.SD,
  	`Run 26 SD(\\Umsy)` = Run.26.SD,
  	`\\% Diff ` = Diff.SD
  )  %>%
  csas_table(
    format = "latex",
    escape = FALSE, 
    font_size = 10,
    align = c("l", rep("r", 6)),
    caption = cap 
  ) %>%
  kableExtra::column_spec(2:7, width = "1.5cm")
```


## Summary

HBM analysis provides an effective approach to formulating priors for key parameters in Bayesian ecological models and has often been applied to estimate productivity parameters for Pacific and Atlantic salmon and other fish species populations [@PrevostOthers2003; @MichielsensMcAllister2004; @SuPetermanHaeseker2004; @Clark2004; @ForestOthers2010; @PulkkinenOthers2011].  The diagnostics shown in this appendix which are routine to HBM analysis [e.g., @GelmanOthers2004; @MichielsensMcAllister2004; @ForestOthers2010] support the basic HBM assumption of exchangeability of the datasets from all 18 stocks with regards to the Ricker  $a$ parameter.  We did not find evidence to support the notion that the two enhanced stocks have consistently different productivity than the non-enhanced stocks.  This is for example based on results (1) from both HBM and non-HBM runs shown in Table \@ref(tab:HBMShrinkageVal) where the posterior means for the Ricker $a$ parameter for the two enhanced stocks were neither consistently higher nor lower than estimates from the 16 non-enhanced stocks, and (2) from the jackknife analysis which showed that the posterior predictive distribution for Ricker $a$ was highly insensitive to leaving out the two enhanced stocks, either one at a time or both at the same time (Figure \@ref(fig:jackProd)).  

Comparisons from the non-HBM and HBM also show that there was a moderate but not extreme amount of shrinkage in Ricker $a$ parameter estimates, where the maximum percentage change in Ricker $a$ was no more than 20% and less than 10% in 13 of the 18 stocks when going from the non-HBM to the HBM.  Shrinkage is to be expected in HBM analysis and the amount of shrinkage found here was not excessive and not so for the two enhanced stocks.  The posterior SDs of the Ricker $a$ parameter for the two enhanced stocks from the non-HBM and HBM (Table \@ref(tab:HBMShrinkageVal)) were also neither consistently larger nor smaller than the posterior SDs for this parameter for the 16 wild stocks.  The estimates of derived parameters such as \Smsy for the two enhanced stocks were also not excessively imprecise with posterior CVs for \Smsy being 0.56 for Pinkut and 0.37 for Fulton (Table \@ref(tab:SenRun2)).  These posterior CVs are well within the range of posterior CVs for fish stock parameters commonly estimated using Bayesian methods. <!--These results thus also refute the notion that due to lack of contrast in the spawner data from the practice of channel loading, the parameter estimates obtained from fitting a Ricker model to their stock recruit data will be excessively imprecise.  -->

Estimation of common shared year effects showed that the estimated effects were statistically significant with 95% PIs not overlapping with zero for 18 of the 55 years.  The estimated effects were highly pronounced in some years, and could change abruptly and considerably in relatively few years.  For example, the estimated effects went from the absolute minimum to the absolute maximum extreme in three years, i.e., -1.37 in 1994 to +1.02 in 1997.  And the most pronounced year effect of all could be linked to epizootic disease event, e.g., in 1994, indicating that at least some of the estimated effects could be attributed to ecological events and the notion that the estimated effects were all due to stock assessment errors is unlikely.  

The above results on common shared year effects suggest that caution is needed should it be of interest to implement random walk models for the Ricker $a$ parameter.  Random walk models typically assume that there exists positive correlation between adjacent years, e.g., for the Ricker $a$ parameter, and tend to provide smoothed trajectories of parameter estimates.  When estimates of common shared year effects from models that exclude random walk jump abruptly been years and shift from minimum to maximum value in only a few years, bias in annual estimates of the Ricker $a$ parameter could thus be expected from random walk models for this parameter.  The common shared year effect also suggested, despite frequent extreme variation between years, extended periods of on average potentially higher productivity in the 1980s to early 1990s and lower than average productivity from 2003-2014.  Estimates of quantities of interest such as \Smsy were also moderately sensitive to the inclusion and exclusion of common shared year effects in the HBM (Table \@ref(tab:SenRun3))).  

Careful attention to how the prior for \Smax was applied in MCMC was also an important consideration in the analysis.  In MCMC integration, values for estimated parameters in Markov Chains even after burn in can wander considerably and occasionally jump to extreme values well outside of the area of support of the data when no constraints are imposed.  The presence of extreme values in approximations of posteriors from MCMC can potentially cause pronounced bias in the estimated parameters.  We found that this was the case in the application of the non-HBM and HBM and extreme parameter values and the incidence in MCMC chains of quantities of interest such as Smsy could be eliminated by implementation of upper and lower bounds for key parameters such as \Smax or Ricker $\beta$.  It is thus appropriate to apply upper and lower bounds for key parameters in MCMC code to prevent these rare but extreme values from occurring and biasing posterior results.  
