# BIAS-CORRECTED BENCHMARK ESTIMATES {#BiasCorrectedBM}


## Nass Summary Tables - Bias Corrected

### Nass Smsy

(ref:SmsyLtAvgNassBC) Comparison of bias-corrected aggregate and stock-level Smsy estimates: Nass / Long-term average productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SmsyLtAvgNassBC, echo = FALSE, results = "asis"}

table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "LTAvg",BM == "Smsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SmsyLtAvgNassBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```



(ref:SmsyRecentNassBC) Comparison of bias-corrected aggregate and stock-level Smsy estimates: Nass / Recent productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SmsyRecentNassBC, echo = FALSE, results = "asis"}


table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "Now",BM == "Smsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SmsyRecentNassBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```


\clearpage
### Nass Sgen


(ref:SgenLtAvgNassBC) Comparison of bias-corrected aggregate and stock-level Sgen estimates: Nass / Long-term average productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SgenLtAvgNassBC, echo = FALSE, results = "asis"}

table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "LTAvg",BM == "Sgen.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SgenLtAvgNassBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```



(ref:SgenRecentNassBC) Comparison of bias-corrected aggregate and stock-level Sgen estimates: Nass / Recent productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SgenRecentNassBC, echo = FALSE, results = "asis"}


table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "Now",BM == "Sgen.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SgenRecentNassBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```


\clearpage

### Nass Umsy

(ref:UmsyLtAvgNassBC) Comparison of bias-corrected aggregate and stock-level Umsy estimates: Nass / Long-term average productivity.  Table also lists the range and median across stock-level estimates.

```{r UmsyLtAvgNassBC, echo = FALSE, results = "asis"}

table.in <-  umsy.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "LTAvg",BM == "Umsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:UmsyLtAvgNassBC)") %>%
    kableExtra::row_spec(c(1,4), hline_after = TRUE) 

```



(ref:UmsyRecentNassBC) Comparison of bias-corrected aggregate and stock-level Umsy estimates: Nass / Recent productivity.  Table also lists the range and median across stock-level estimates.

```{r UmsyRecentNassBC, echo = FALSE, results = "asis"}

table.in <-  umsy.bm.tab.src %>% dplyr::filter(Aggregate=="Nass",Scenario == "Now",BM == "Umsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:UmsyRecentNassBC)") %>%
    kableExtra::row_spec(c(1,4), hline_after = TRUE) 

```





\clearpage
## Skeena Wild Summary Tables - Bias Corrected

### Skeena Wild Smsy

(ref:SmsyLtAvgSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Smsy estimates: Skeena Wild / Long-term average productivity. Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SmsyLtAvgSkeenaWildBC, echo = FALSE, results = "asis"}

table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "LTAvg",BM == "Smsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SmsyLtAvgSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```


\clearpage
(ref:SmsyRecentSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Smsy estimates: Skeena Wild / Recent productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SmsyRecentSkeenaWildBC, echo = FALSE, results = "asis"}


table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "Now",BM == "Smsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SmsyRecentSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```


\clearpage
### Skeena Wild Sgen


(ref:SgenLtAvgSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Sgen estimates: Skeena Wild / Long-term average productivity. Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added. 

```{r SgenLtAvgSkeenaWildBC, echo = FALSE, results = "asis"}

table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "LTAvg",BM == "Sgen.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SgenLtAvgSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```


\clearpage
(ref:SgenRecentSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Sgen estimates: Skeena Wild / Recent productivity.  Stocks are sorted based on median estimate. Mean and median estimates were summed across stocks as a comparison to the aggregate fit, but percentiles can not be simply added.  

```{r SgenRecentSkeenaWildBC, echo = FALSE, results = "asis"}


table.in <-  abd.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "Now",BM == "Sgen.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:SgenRecentSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,3), hline_after = TRUE) 

```




\clearpage

### Skeena Wild Umsy

(ref:UmsyLtAvgSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Umsy estimates: Skeena Wild / Long-term average productivity.  Table also lists the range and median across stock-level estimates.

```{r UmsyLtAvgSkeenaWildBC, echo = FALSE, results = "asis"}

umsy.bm.tab.src <- read_csv("data/SummaryTables_UMSY.csv")

table.in <-  umsy.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "LTAvg",BM == "Umsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:UmsyLtAvgSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,4), hline_after = TRUE) 

```


\clearpage
(ref:UmsyRecentSkeenaWildBC) Comparison of bias-corrected aggregate and stock-level Umsy estimates: Skeena Wild / Recent productivity.  Table also lists the range and median across stock-level estimates.

```{r UmsyRecentSkeenaWildBC, echo = FALSE, results = "asis"}

table.in <-  umsy.bm.tab.src %>% dplyr::filter(Aggregate=="SkeenaWild",Scenario == "Now",BM == "Umsy.c") %>% select(-Aggregate,-Scenario,-BM) %>%
							mutate_if(is.numeric,function(x){prettyNum(round(x), big.mark=",")})
	
table.in[table.in == "NA"] <- "-"

table.in %>%
   mutate_at(1,function(x){gsub("&", "\\\\&", x)}) %>% 
   mutate_at(1,function(x){gsub("%", "\\\\%", x)}) %>%
csas_table(format = "latex", escape = FALSE, font_size = 9, align = c("l",rep("r",6)),
                  caption = "(ref:UmsyRecentSkeenaWildBC)") %>%
    kableExtra::row_spec(c(1,4), hline_after = TRUE) 

```


